---
title: "Homework 4"
author: "Virginia Sanson"
date: "4 April 2023"
output:
  pdf_document:
    toc: no
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
header-includes: \usepackage{booktabs}
---
```{r , include=FALSE}
load("Hw4_workspace.Rdata")
load("4_workspace.Rdata")
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata, scales,
               kableExtra, rdrobust)
library(rdrobust)
```

\newpage
\noindent Question 1

```{r}

q1.plot

```
These ranges of plan counts seems sufficient - I assumed plans would be in the 20-50 range. 

\newpage
\noindent Question 2

```{r}

q2.plot

```

Over time, the distribution of higher star ratings (ratings of 4-5) has increased. Over the years, there are fewer low ratings and a higher concentration of high ratings. 

\newpage
\noindent Question 3

```{r}

avg.benchmark

```
Over the years, the average benchmark payment has risen and dipped,overall decreasing to ~$780. 

\newpage
\noindent Question 4

```{r}

ma.share

```
The share of Medicare Advantage has increased in popularity, gradually increasing from 2008 to 2015. This inversely correlates with the benchmark payments. 

\newpage
\noindent Question 5

```{r}

print(table(final.data.2009$star_rating_category))

```

\newpage
\noindent Question 6

```{r}

regression6_1

```

```{r , include=FALSE}

regression6_2

```

```{r , include=FALSE}

regression6_3

```

\newpage
\noindent Question 7

```{r , include=FALSE}

rdrobust(y=ma.rd6$mkt_share, x=ma.rd6$score1, c=0,
                  h=0.1, p=1, kernel="uniform", vce="hc0",
                  masspoints="off")


```

```{r , include=FALSE}

rdrobust(y=ma.rd6$mkt_share, x=ma.rd6$score1, c=0,
                  h=0.12, p=1, kernel="uniform", vce="hc0",
                  masspoints="off")


```

```{r , include=FALSE}

rdrobust(y=ma.rd6$mkt_share, x=ma.rd6$score1, c=0,
                  h=0.13, p=1, kernel="uniform", vce="hc0",
                  masspoints="off")
```

```{r , include=FALSE}

rdrobust(y=ma.rd6$mkt_share, x=ma.rd6$score1, c=0,
                  h=0.14, p=1, kernel="uniform", vce="hc0",
                  masspoints="off")

```

```{r , include=FALSE}

rdrobust(y=ma.rd6$mkt_share, x=ma.rd6$score1, c=0,
                  h=0.15, p=1, kernel="uniform", vce="hc0",
                  masspoints="off")


```

The findings are very sensitive to the choice of bandwidth. Even incremental changes in bandwidth result in large changes to the star rating effect on enrollments. Unfortunately, I could not summarize my results in a graph but above are the RD estimator results for the comparisons. 
\newpage
\noindent Question 8

```{r}

rdplot(y=ma.rd6$mkt_share, x=ma.rd6$score1, binselect = "es", 
                   title = "RD Plot: Market Share", x.label="Summary Score", 
                   y.label="Market Share", masspoints="off")

```

```{r}

rdplot(y=ma.rd6$mkt_share, x=ma.rd6$score1, binselect = "es", 
                   title = "RD Plot: Market Share", x.label="Summary Score", 
                   y.label="Market Share", masspoints="off")

```

```{r}

rdplot(y=ma.rd6$mkt_share, x=ma.rd6$score3, binselect = "es", 
                   title = "RD Plot: Market Share", x.label="Summary Score", 
                   y.label="Market Share", masspoints="off")


```
The distribution of the running variable before and after the relevant threshold values seems to not change drastically. It was a lor wider before, but I do not believe contracts appear to manipulate the running variable. 

\newpage
\noindent Question 9

Attempted this code again, with tweaks:

summary1 <- ma.rd6 %>% filter(score1>-0.25 & score1<0.25)
summary1$above <- ifelse(summary1$score1 > 0, 1,0 )
tab9 <- summary1 %>% group_by(above) %>% summarize(prop_partd = mean(partd == "Yes"))

However, I predict that plans just above the threshold values would not have different characteristics than contracts just below the threshold values. 
\newpage
\noindent Question 10

With my results in ATE 1-4, and predictions for question 5, I predict that increasing star ratings generally lead to increases in enrollments. 

