---
title: "ECON 470 Homework 4"
author: "Virginia Sanson"
output: pdf_document
date: "2023-04-02"
---

```{r , include=FALSE}
load("Hw4_workspace.Rdata")
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata, scales,
               kableExtra)
```

\newpage
\noindent Question 1

```{r , include=FALSE}

q1.plot

```
Do you think that the number of plans is sufficient, too few, or too many?

\newpage
\noindent Question 2

```{r , include=FALSE}

q2.plot

```

How has this distribution changed over time?

\newpage
\noindent Question 3

```{r , include=FALSE}

q3.plot

```
How much has the average benchmark payment risen over the years?

\newpage
\noindent Question 4

```{r , include=FALSE}

q4_plot

```
Has Medicare Advantage increased or decreased in popularity? How does this share correlate with benchmark payments?

\newpage
\noindent Question 5

```{r, include=FALSE}

print(table(final.data.2009$star_rating_category))

```

```{r , include=FALSE}

print(table_5)

```

\newpage
\noindent Question 6

```{r , include=FALSE}

summary(regression6_1)
summary(regression6_2)
summary(regression6_3)

```

\newpage
\noindent Question 7

```{r , include=FALSE}

q2.plot

```
How sensitive are your findings to the choice of bandwidth?

\newpage
\noindent Question 8

```{r , include=FALSE}

graph_7a

```

```{r , include=FALSE}

graph_7b

```

```{r , include=FALSE}

graph_7c

```
In other words, look at the distribution of the running variable before and after the relevent threshold values. What do you find?

\newpage
\noindent Question 9

```{r , include=FALSE}



```

\newpage
\noindent Question 10

Summarize your findings from 1-5. What is the effect of increasing a star rating on enrollments? Briefly explain your results.

